Estimating the Attack Ratio of Dengue Epidemics under Time-varying Force of Infection using Aggregated Notification Data

### 2015-06-01 Presentations/Dinamica de Vetores-SP-2015/dengueARS0.tex
updated presentation for Talk at UPMC

\author{Flávio Codeço Coelho and Luiz Max Carvalho}
\title{Estimating the Attack Ratio of Dengue Epidemics under Time-varying 
Force of Infection using Aggregated Notification Data}
\date{11-02-2015}
\institute [EMAp, FGV]{Escola de Matemática Aplicada,   Fundação Getúlio Vargas}

%\logo{\includegraphics[height=2cm]{./fb1.png}}
\begin{document}
 \begin{frame}
\titlepage
\end{frame}

@@

Ederer and Mantel (1974)~\cite{mantel} show that one can construct a $100\alpha 
\%$ confidence interval for \rr by noting that
\begin{equation}
\label{eq:confRt}
 R_t^{(L)} = \frac{\theta_t^{(L)}}{(1-\theta_t^{(L)})} \quad \text{and} \quad 
R_t^{(U)} = \frac{\theta_t^{(U)}}{(1-\theta_t^{(U)})}\\
\end{equation}
\end{frame}

@@

\end{frame}
\end{document}

>>>>

\author{Flávio Codeço Coelho and Luiz Max Carvalho}
\title{Estimating the Attack Ratio of Dengue Epidemics under Time-varying 
Force of Infection using Aggregated Notification Data}
\date{May 1st, 2015}
\institute [EMAp, FGV]{Applied Mathematics School,   Fundação Getúlio Vargas}

\logo{\includegraphics[width=\beamer@sidebarwidth]{./fb1.png}}
\begin{document}
 \begin{frame}
\titlepage
\end{frame}

@@

Ederer and Mantel (1974)~\cite{mantel} show that one can construct a $100\alpha 
\%$ confidence interval for \rr by noting that
\begin{equation}
\label{eq:confRt}
 R_t^{(L)} = \frac{\theta_t^{(L)}}{(1-\theta_t^{(L)})} \quad \text{and} \quad 
R_t^{(U)} = \frac{\theta_t^{(U)}}{(1-\theta_t^{(U)})}
\end{equation}
\end{frame}

@@

\end{frame}
\begin{frame}
 \frametitle{Collaboration possibilities}
 \begin{itemize}
  \item Relaxing other simplifying assumptions in classical epidemiological 
models.
\item Looking into modeling spatio-temporal dynamics taking into account 
Environmental stock of eggs.
\item Separating noise from relevant varibility in observational data, and 
finding new ways of integrating it into models.
 \end{itemize}

\end{frame}
\begin{frame}

 \begin{center}
\begin{Huge}Thank you!           \end{Huge} \end{center}
\end{frame}

\end{document}
